---
title: "Statistical Inference Project Part 2"
author: "Collin Mitchell"
date: "August 23, 2015"
output: html_document
---

# Overview
This paper is to discuss an Analysis of the ToothGrow Dataset within the R Library.
A prelimenary overview of the data shows that it is comprised of Three Columns: Length of Growth, Suppliment, and the Dosage.

The most obvious beginning function to get an initial understanding is the Summary function.
```{r}
# load the data and display the summary.
data("ToothGrowth")
summary(ToothGrowth)
```


While this is interesting, what we really want to know is how effective the suppliments are.
So, how many different types are there? The suppliments are: `r levels(as.factor(ToothGrowth$supp))`.

These two abbreviations stand for Viatmin C and Orange Juice, respectively.
We want to split the data up based on these two factors. So, where does the split occur?
```{r}
match("OJ", ToothGrowth$supp)
```
So, the first index for Orange Juice is 31, out of `r length(ToothGrowth$supp)`. That means the data is split right in half.

And, we can visualize this using the below statements.

```{r}
# pull out the data to make it easier to plot via reference
toothLength <- ToothGrowth$len
toothDose   <- ToothGrowth$dose

par(mfrow = c(1,2))
vitaminC <- plot(toothLength[ 1:30], toothDose[ 1:30], main="Vitamin C Dosage", xlab="Tooth Length", ylab="Suppliment Dosage")
orangeJ  <- plot(toothLength[31:60], toothDose[31:60], main="Orange Juice Dosage", xlab="Tooth Length", ylab="Suppliment Dosage")
```

From the graphs, is looks like Orange Juice is a much better suppliment for teeth than just Vitamin C at lower doses. However, as the volume of Vitamin C increases, we can see that the growth of the teeth supstantially increases beyond what Orange Juice does.


```{r}
library(reshape2)
alteredTeeth <- dcast(ToothGrowth, supp + len ~ dose)
t.test(len ~ supp, paired = F, var.equal = T, data = alteredTeeth)$conf
```
From the test, it seems that the two sets of data are not comparable.
 