---
title: "Statistical Inference Course Project"
author: "Collin Mitchell"
date: "August 23, 2015"
output: html_document
---

# Overview
This paper was created to explore the Central Limit Theorem of Statistics.
For reference, the definition 

## Points to Prove
1. Show the sample mean and compare it to the theoretical mean of the distribution.
2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
3. Show that the distribution is approximately normal.

Mean of the exponential function is 1/lambda.

There are a few requirements:

```{r}
n      = 40
lambda = .2
```

What is the difference between 1000 random distributions and the average of 40 simulations

```{r, echo=FALSE}
hist(rexp(1000, lambda))

means = NULL
for(i in 1:1000) means = c(means, mean(rexp(40)))
hist(means)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


Overview: In a few (2-3) sentences explain what is going to be reported on.
Simulations: Include English explanations of the simulations you ran, with the accompanying R code. Your explanations should make clear what the R code accomplishes.
Sample Mean versus Theoretical Mean: Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers.
Sample Variance versus Theoretical Variance: Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.
Distribution: Via figures and text, explain how one can tell the distribution is approximately normal.

```{r}
